On behalf of the International Committee on Computational Linguistics (ICCL), we are delighted to welcome you to the 31st International Conference on Computational Linguistics: COLING 2025, held in Abu Dhabi, United Arab Emirates.\\

Unlike the previous 30 editions of COLING, which were held every two years, this COLING takes place only eight months after the preceding COLING conference in Turin, Italy, which was (exceptionally) joint with the LREC conference. What might look like a not very clever move (to say the least) – especially in view of the density of the major conferences in our field in summer and autumn – was motivated by the goal to disentangle LREC and COLING, the two major  biannual conferences, which have, despite all their differences, a lot in common and therefore also share a significant percentage of attendees.  From now on, COLING will be held in odd years (as had already been the case from 1965 to 1973), while LREC will continue to be held in even years. In addition to this change, COLING 2025 introduces another novelty: the main conference is in-person only, but, in order to facilitate the participation of researchers who cannot travel to Abu Dhabi for whatever reason, we have introduced a separate, entirely virtual component of the conference. The virtual poster session will take place the week after the in-person part, and will enable all authors to present their papers.\\

Our colleagues from the Mohamed bin Zayed University of Artificial Intelligence in Abu Dhabi generously offered to host COLING 2025, and what month is better to hold a conference in the United Arab Emirates than January! And here we are! Obviously, the short organization time has been a challenge for the entire Organizing Committee.  The Program Chairs Hend Al-Khalifa, Marianna Apidianaki, Barbara Di Eugenio, and Steven Schockaert, have managed to organize the submission, reviewing, selection, and scheduling of a large number of papers in an exceptionally short time frame. Our Local Committee Chairs Preslav Nakov, Nizar Habash, Yova Kementchedjhieva, Monojit Choudhury, Ahmed Dabbagh, Ekaterina Kochmar, Alham Fikri Aji, and Teresa Lynn have paid attention to all other organizational details (venue, accommodations, visas, budget). Especially Preslav was in demand in all matters, and in all of our numerous meetings. Jenn Rachford (R \& R Planning) took over a substantial part of the organization of the conference and guided us with her professionalism, experience and wisdom. \\

However, we must not forget the hard work by the other members of our Organizing Committee: \\

Workshop Chairs: Katsuhito Sudoh and Mo El-Haj; Tutorial Chairs: Djamé Seddah and Shaonan Wang; Demonstration Chairs: Brodie Mather and Mark Dras; Industrial Track Chairs: Kareem Darwish and Apoorv Agarwal; Ethics Chairs: Zeerak Talat and Su Lin Blodgett; Publicity \& Social Media Chairs: Sakhar AlKhereyf and Baotian Hu; Website Chairs: Hasan Iqbal and Zain Muhammad Mujahid; Publication Chairs: Emily Allaway and Guillermo Cámbara; Volunteer Chair: Artem Shelmanov; Virtual Infrastructure Chairs: Tuhin Chakrabarty and Alexander Shvets; Birds-of-a-Feather Chairs: Hawau Olamide Toyin and Mukund Choudhary; and Best Paper Committee Chairs: Kevin Duh and Aline Villavicencio. All of them had to put in an extra work shift in order to be able to cope with the very demanding time constraints. We would like to take the opportunity to thank all of them! We could not have wished for a better or more dedicated team to work alongside. We would also like to thank our generous sponsors: The Abu Dhabi Convention and Exhibition Center, The Mohamed bin Zayed University of Artificial Intelligence (MBZUAI), the Technology Innovation Institute, New York University Abu Dhabi, Inception, Baidu, Google, Toloka AI, and Applied AI. \\

The result of this tremendous joint effort is an exciting high-quality program of 853 papers at the main conference, in addition to 22 workshops, 9 tutorials, and a winter school. In the in-person part of the conference program, we maintain the spirit of COLING and offer a number of different excursions that, as we are sure, will stimulate the social interaction between the attendees and allow them to immerse themselves into the cultural attractions of the United Arab Emirates.\\

Last but not least, we would like to thank each and every one of you for making COLING 2025 such a success by submitting high quality papers and demos, organizing workshops and tutorials on hot topics in our field, serving as Senior Area Chairs, Area Chairs, and Reviewers or Invited Speakers, and by joining us in Abu Dhabi.\\

Enjoy COLING 2025 in Abu Dhabi!\\

Owen Rambow and Leo Wanner

General Chairs of COLING 2025
