Welcome to the 31st International Conference on Computational Linguistics! \\

COLING 2025 is an in-person event which will take place in the beautiful historical city of Abu Dhabi. The conference includes a virtual 2-day event which will take place online shortly after the in-person conference. \\

COLING 2025 received 2,530 direct submissions and 193 papers committed via the ACL Rolling Review (ARR) route. Of the direct submissions, 2,335 were reviewed: 1,922 long papers, of which 605 were accepted (31.5\%), and 413 short papers, of which 85 were accepted (20.6\%). From the papers that were committed via ARR, we accepted 58 long papers, out of a total of 167 (34.7\%), and 12 short papers, out of a total of 26 (46.2\%). Across all categories, we have accepted a total of 760 papers (30.1\%). We are gratified to note the great interest and enthusiasm that researchers in our community have shown for COLING 2025. We would like to thank all authors who submitted their work to the conference, and congratulate those whose papers were accepted for presentation. \\

We would like to thank the amazing pool of 2,418 reviewers, who made the conference possible and devoted their time to the careful assessment of the papers assigned to them, and in particular the emergency reviewers who stepped in at the last moment. Much of the heavy lifting in the review process fell on the 62 Senior Area Chairs and the 274 Area Chairs; we are extremely grateful to them for their efforts and time. We also want to thank the OpenReview team for their help in handling papers submitted to COLING 2025 via ARR. We would like to express our gratitude to our Best Paper Awards Committee Chairs, Kevin Duh (Johns Hopkins University, USA) and Aline Villavicencio (University of Exeter and University of Sheffield (UK), Federal University of Rio Grande do Norte (Brazil)), and to the Awards Committee members. \\

The COLING 2025 program features three exciting keynote speakers: Katrin Erk (University of Texas at Austin, USA), Emmanuel Dupoux (EHESS, META, France), and Partha Talukdar (Google DeepMind and IISc Bangalore, India).\\

To everyone mentioned above, we again express our deepest thanks for helping in so many different ways to make COLING 2025 a memorable event. We hope that you will enjoy the conference!\\

Marianna Apidianaki

Hend Al-Khalifa

Barbara Di Eugenio

Steven Schockaert

COLING 2025 Program Committee Co-Chairs
